---
always_allow_html: true

---


# FOLIAR NUTRIENT DIAGNOSIS REPORT

* Reporting date/time: `r Sys.time()`

#### *Caution!* Please note that this report was made through the proto-version of *FOLIAR NUTRIENT DIAGNOSIS*, so the diagnosis and fertilizer prescription might contain errors.

## Diagnosis completed for:

* Name: `r paste(input$FirstName, input$LastName)`
* Organization: `r input$Org`
* Address: `r input$Addr_1` `r input$Addr_2` `r input$Addr_3` `r input$Addr_4`
* Foliar sampling date: `r input$samp_date`
* Analytical Laboratory: `r input$Lab_type`


## Site/Stand Information:

* Sample ID: `r input$SampID`
* Species: `r input$spp`
* Site Location: `r input$SiteID`
* BEC Subzone: `r paste(input$BEC_zone, input$BEC_subz)`
* Site series: `r input$BEC_site`
* Elevation (m): `r input$Elev`
* Mapsheet: `r input$Map`
* Opening: `r input$Open`
* Stand age (yrs): `r input$Age`
* Stand origin: `r switch(input$Origin, "Plantation" = "Plantation", "Natural_F"="Natural (fire origin)", "Natural_H"= "Natural (harvest origin)")`
* Site index (m): `r input$SI`
* Percent Live Crown: `r input$Crown`
* Recently (past two years) fertilized (Yes/No): `r input$Prev_fert`

```{r out.width='100%', echo=FALSE, warning=FALSE, message=FALSE}

lng <- ifelse(input$Long_deg=="", -123.3666667, as.numeric(input$Long_deg) + as.numeric(input$Long_min)/60)
lat <- ifelse(input$Lat_deg=="", 48.4166667, as.numeric(input$Lat_deg) + as.numeric(input$Lat_min)/60)


samp_loc <- data.frame(lng = lng, lat = lat)

map_borders <- c(bottom  = lat - 0.4, 
                 top     = lat + 0.4,
                 left    = lng - 0.6,
                 right   = lng + 0.6)
map <- get_stamenmap(map_borders, maptype = "toner-lite")
ggmap(map) +
    geom_point(data=samp_loc, mapping = aes(x = lng, y = lat, col = "red", size = 200, alpha = 1),
show.legend = FALSE) +  xlab("Longitude") + ylab("Latitude") + ggtitle('Sample Location') +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3))


```


## Foliar Sampling Information:

* Crown position: `r input$Cr_pos`
* Foliar age: `r switch(input$Leaf_age, "Cur_yr" = "Current year", "1_yr"="1-year-old", "1-yr-more"= "Greater than 1-year-old", "Mixed ages" = "Mixed ages")`
* Individual/composite Sample: `r ifelse(input$Diag_base=="Indv_sam", "Individual sample" ,"Composite sample")`
`r if(input$Diag_base=="Comp_sam") paste("* Number of trees per composite: ", input$Comp_Number )`
* Pertinent site/stand information: `r input$Pertinent`



## Foliar Nutrient Data:

```{r, echo=FALSE,warning=FALSE}
suppressWarnings(suppressMessages(library("pander")))   # suppress warnings
panderOptions('table.continues', '')
outtb <- output.table()
colnames (outtb) <- c("Elements", "Measured Values", "Normalized Values", "Deviation from Adequate Level", "Interpretation")
rownames(outtb) <- NULL
pander(outtb, split.table = 100, round=1, style = 'rmarkdown')
```



## COMMENTS:

```{r, echo=FALSE,warning=FALSE}
write_super_comment(spp = input$spp, Lab_type = input$Lab_type, Crown = input$Crown,
                                                    B_value = B_norm(), N_K_value = N_norm()/K_norm(),
                                                    Cr_pos = input$Cr_pos, samp_date = input$samp_date, 
                                                    Diag_base = input$Diag_base, 
                                                    Comp_Number = as.numeric(input$Comp_Number),
                                                    Leaf_age = input$Leaf_age, Pertinent = input$Pertinent)
```


## DIAGNOSIS:

*see "Comments" above for factors that may affect the foliar nutrient diagnosis*

### Nitrogen (N):
`r concat_comments_nutrients(spp = input$spp, "N", N_norm(), input$Prev_fert, input$Lab_type)`


### Phosphorus (P):
`r concat_comments_nutrients(spp = input$spp, "P", P_norm(), input$Prev_fert, input$Lab_type)`

`r concat_comments_nutrients_ratio(spp = input$spp, "N:P", N_norm()/P_norm(), P_norm(), SO4_norm(), input$Prev_fert)`

### Potassium (K):
`r concat_comments_nutrients(spp = input$spp, "K", K_norm(), input$Prev_fert, input$Lab_type)`

`r concat_comments_nutrients_ratio(spp = input$spp, "N:K", N_norm()/K_norm(), K_norm(), SO4_norm(), input$Prev_fert)`

### Calcium (Ca):
`r concat_comments_nutrients(spp = input$spp, "Ca", Ca_norm(), input$Prev_fert, input$Lab_type)`


### Magnesium (Mg):
`r concat_comments_nutrients(spp = input$spp, "Mg", Mg_norm(), input$Prev_fert, input$Lab_type)`
`r concat_comments_nutrients_ratio(spp = input$spp, "N:Mg", N_norm()/Mg_norm(), Mg_norm(), SO4_norm(), input$Prev_fert)`

### Sulphur (S):
`r concat_comments_nutrients(spp = input$spp, "S", S_norm(), input$Prev_fert, input$Lab_type)`
`r concat_comments_nutrients_ratio(spp = input$spp, "N:S", N_norm()/S_norm(), S_norm(), SO4_norm(), input$Prev_fert)`
`r output$diag_SO4 <- renderText(concat_comments_nutrients(spp = input$spp, "SO4", SO4_norm(), input$Prev_fert, input$Lab_type))`

### Copper (Cu):
`r concat_comments_nutrients(spp = input$spp, "Cu", Cu_norm(), input$Prev_fert, input$Lab_type)`


### Zinc (Zn):
`r concat_comments_nutrients(spp = input$spp, "Zn", Zn_norm(), input$Prev_fert, input$Lab_type)`

### Iron (Fe):
`r concat_comments_nutrients(spp = input$spp, "Fe", Fe_norm(), input$Prev_fert, input$Lab_type)`

### Manganese (Mn):
`r concat_comments_nutrients(spp = input$spp, "Mn", Mn_norm(), input$Prev_fert, input$Lab_type)`

### Boron (B):
`r concat_comments_nutrients(spp = input$spp, "B", B_norm(), input$Prev_fert, input$Lab_type)`



##  FERTILIZER PRESCRIPTION:

```{r, echo=FALSE,warning=FALSE}
write_super_prescription (spp = input$spp, Prev_fert = input$Prev_fert, N_value = N_norm(), 
                                                            Lab_type = input$Lab_type, SO4_value = SO4_norm(),
                                                            N_S_value = N_norm()/S_norm(), Cu_value = Cu_norm(),
                                                            Zn_value = Zn_norm(), Fe_value = Fe_norm(), 
                                                            Mn_value = Mn_norm(), P_value = P_norm(), 
                                                            N_P_value = N_norm()/P_norm(), K_value = K_norm(),
                                                            N_K_value = N_norm()/K_norm(), Ca_value = Ca_norm(), 
                                                            Mg_value = Mg_norm(), N_Mg_value = N_norm()/Mg_norm(),
                                                            B_value = B_norm())

```



